DDM: Distributed Decision Making Model for Dynamic Formation of Web services Communities

### 2014-12-21 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
%\title{A Distributed Mechanism for Intelligent \\ Web Service Community Formation}
\title{DM: A Distributed Decision Making Model for \\ Dynamic Formation of Web services Communities}
%
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%
%
%\IEEEcompsocitemizethanks is a special \thanks that produces the bulleted
% lists the Computer Society journals use for "first footnote" author
% affiliations. Use \IEEEcompsocthanksitem which works much like \item
% for each affiliation group. When not in compsoc mode,
% \IEEEcompsocitemizethanks becomes like \thanks and
% \IEEEcompsocthanksitem becomes a line break with idention. This
% facilitates dual compilation, although admittedly the differences in the
% desired content of \author between the different types of papers makes a
% one-size-fits-all approach a daunting prospect. For instance, compsoc
% journal papers have the author affiliations above the "Manuscript
% received ..."  text while in non-compsoc journals this is reversed. Sigh.

@@

Web services are loosely-coupled business applications willing to cooperate in distributed settings within different groups called communities. Communities aim to provide web services with better visibility, efficiency, market share and total payoff. A number of mechanisms and models have been recently proposed to aggregate web
services and make them cooperate within their communities. However, the solutions mostly focus on short term goals. Moreover, these solutions generally suffer from high computational complexity, which makes decision making impossible in an on-demand fashion. In this paper, we propose a strategic decision making mechanism that regulates web service agents' decision making process in terms of cooperating with one another. This model first generates a trained set of data based on information obtained from large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc. Utilizing the training model, the decision making mechanism implements a decision tree of possible viable strategies and their long-term expected utility gain.
%Utilizing the training model, the decision making mechanism implements a decision tree with an estimation of long-term utility gain for the web services. Communities can used the trained model and instantly choose best-response strategies considering their long-term gain. 
Our findings show that using this data, communities of web services can efficiently find the appropriate web service to invite cooperating with them as well as a single web service can find best communities to target joining them. In further details, after being trained, web services get to compute expectations as utilities they would gain while cooperating with communities of different characteristics. In contrast, communities can consider the training into account and analyze the characteristics of different individual web services and make prudent decisions while inviting a web service to join or accepting a join inquiry initiated from a web service. In general, DLISA equips web services with efficient methods of foreseeing how their choices of actions would impact their long-term and short-term goals, therefore opting for best decision available. The experimental results show that our algorithms provide web services and community owners, in real-world-like environments, with applicable and near-perfect decision making mechanisms.

%In the last few years, communities of services have been studied in a certain numbers of proposals as virtual pockets of similar expertise. The motivation is to provide these services with high chance of discovery through better visibility, and to enhance their capabilities when it comes to provide requested functionalities. We introduce DLISA (Machine Learning-based Intelligent Service Agents) community framework that operates based on a trained model that regulates web service agents' decision making process in terms of cooperating with one another. This model uses the trained data in the form of information obtained from large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc. The training model deploys logistic regression algorithm to build hypothesis function that can thoroughly address the aforementioned research problems. Our findings show that communities of web services can efficiently find the appropriate web service to invite cooperating with them as well as a single web service can find best communities to target joining them. In further details, after being trained, web services get to compute expectations as utilities they would gain while cooperating with communities of different characteristics. In contrast, communities can consider the training into account and analyze the characteristics of different individual web services and make prudent decisions while inviting a web service to join or accepting a join inquiry initiated from a web service. In general, DLISA equips web services with efficient methods of foreseeing how their choices of actions would impact their long-term and short-term goals, therefore opting for best decision available.

@@

% Note that keywords are not normally used for peer review papers.
\begin{keywords}
Web services; Community of services; Machine Learning;
\end{keywords}}

@@

In this paper, we introduce DLISA (Distributed Learning-based Intelligent Service Agents) community framework that operates based on a decision model that regulates web service agents' decision making process in terms of cooperating with one another. The decision model in extracted from a data model in the form of information obtained from a large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc. 
%The training model deploys a logistic regression algorithm to build a hypothesis function that can thoroughly address the aforementioned research problems. 
The decision model utilizes web services with enough information to efficiently decide and predict the outcome of their moves amongst the available services accessible to them. This model works in distributed manner in which our services are self-sufficient in decision making process and do not rely on a centralized decision maker process. Our findings show that communities of web services can efficiently find the appropriate web service to invite cooperating with them as well as allowing a single web service to find the best communities to join them. Furthermore, the decision model provides web services with expectations of utilities they would gain while cooperating with communities of different characteristics. In contrast, communities can consider the decision model and analyze the characteristics of different individual web services and make prudent decisions when inviting a web service to join or accepting a join inquiry initiated from a web service. In general, DLISA equips web services with efficient methods for foreseeing how their choices will impact their long-term and short-term goals; therefore, opting for best decision available.

In further detail, DLISA is applicable for any sort of intelligent agent-based model. To effectively train web services, we used real data sets to extract web services' individual characteristics and used them to measure outcomes when they cooperate with one another. The data set has been extracted by real-world QoS evaluation results from 142 users on 4,532 Web services on 64 different time slots. Combining these data based on each web service point of view on different time slots, we acquired 5 different unique features for 4,532 web services. Engineering and extracting these features, we gathered functional and cooperative features for both individual web services and communities in different time slots. We were able to investigate the path a web service might take to achieve the best utility out of effective interaction with others. All paths and the outcomes are labeled to be utilized in the training model. Using cross validation sets, web services are able to compute the optimal hypothesis function (using logistic regression) that can be used to predict outcomes of cooperative work with other individual web services or communities. Our findings show that web services equipped with DLISA have by far better outcomes in the form of cooperative service providers than the ones that either do not cooperate or randomly find communities to join.

@@

\section{Preliminaries and Problem Statement}\label{s:preliminaries}
In this section, we first present the architecture of DLISA. We explore the characteristics of intelligent service agents and the features we extract for training. To do this, we first discuss some preliminaries.

@@

	We normalize the range of these features so that each feature contributes approximately proportionately to the final utility outcome value. We subtract the \emph{mean} from each feature then we divide the values of each feature by its \emph{standard deviation}.

@@

\begin{algorithm}
\DontPrintSemicolon
\KwIn{$\langle r, gain^t_{n,n}, CFVS \rangle$ learning rate $r$, $|N \times N \times T|$ gain matrix, community feature vector}
\KwOut{A set of \emph{root} nodes of the decision trees}
$k \gets 1$\;
$nodes[N] \gets$ initialize $N$ tree nodes representing each community in CFVS\;
\For{$t \gets 1$ \textbf{to} $T$} {
	$k \gets 1 + round (r \times t)$\;
  \For{all $C_i \in CFVS$} {
	  \For{all $C_j \in L^t(C_i, k)$} {
      % The "l" before the If makes it so it does not expand to a second line
      \If{$C_i \in L^t(C_j, k)$}{
        $C_k \gets C_i \cup C_j$\;
				add $C_k$ to $CFVS$ set\;
				initiate $node_k$, representing $C_k$\;
				$nodes_i.addChild (node_k)$\;
				$nodes_j.addChild (node_k)$\;
      }
%      \Else{
%        $j \gets j + 1$\;
%      }			
		}
  }
%  $i \gets i + 1$\;
}
\Return{nodes}\;
\caption{{\sc DLISA Decision Tree Algorithm}}
\label{algo:dectree}
\end{algorithm}

\subsection{Decision Tree Creation Complexity}\label{ss:complexity}
Here we analyze the computational complexity of the DLISA decision tree creation algorithm on each time iteration $t$. Computing top $k$ preferred communities for $C_i$ in $L^t(C_i, k)$ requires an $O(n.log(n))$ sort time. $C_i$ has a result set of size $|k|$, and for each of those $k$ communities we need to check against their $k$ top preferred communities. Considering we already have the list sorted, line 6 in algorithm runs $O(k \times n.log(n))$ times. Doing this search for all communities in $|CFVS|$ set $n$ times (line 5), the overall order of complexity of the algorithm in regards with $n$ and $k$ is: $O(k^2 \times n^2.log(n))$.

\section{Experiments}\label{s:experiments}
We implemented DLISA in Java\footnote{Source code of implementation and data is available at: \emph{https://github.com/Marooned202/DLISA}}. We have extracted the set of features for 4532 web services in 64 different time slots through a data set provided by \cite{10.1109/ISSRE.2011.17}. By choosing 86 web services out of these sets and choosing a subset of all possible combinations of sizes 2, 3, and 4 of these 86 web services, we have chosen 10,000 communities and evaluated the feature vectors and utilities they can have in 64 different time slots. This provides us with the initial training feature set of size $|CFVS| = 10,000$ communities. Based on Equation \ref{u_c_load} the utility of these communities are estimated, and the gain matrix $|10000 \times~ 10000|$ of all possible ways of merging these 10,000 communities, is generated\footnote {The template vector and gain matrix generated are available at \emph{https://github.com/Marooned202/DLISA/tree/master/wsds/data/run}}, and each community has the ordered preference among other communities known in the set.

We let communities and web services adopt their strategies based on our $DLISA$ decision making mechanism. Based on the decisions adopted, each community will generate a decision tree profile. We let DLISA run four times with different $r$ rates of 0.05, 0.07, 0.10 and 0.20. With the slow rate of $r = 0.05$, we increase $k$ in Equation \ref{u_c_normal} for every 20 time frames, which will happen only three times in our 64-step experiment. In the case of $r = 0.20$, k increases much faster, at a rate of once every 5 time frames, which increases the complexity of the $L^t(C_i,k)$ search for each community in the $CFVS$ set.

@@

\begin{figure}%[!t]
\centering
\includegraphics[width=3.5in]{figures/utility_gain_r.eps}
\caption{DLISA Utility Gain Value}
\label{utility_gain_value}
\end{figure}

\begin{figure}%[!t]
\centering
\includegraphics[width=3.5in]{figures/utility_ratio_r.eps}
\caption{DLISA Utility Gain Ratio}
\label{utility_gain_ratio}
\end{figure}

@@

\begin{figure}%[!t]
\centering
\includegraphics[width=3.5in]{figures/utility_gain.eps}
\caption{Utility Gain DLISA and Rational}
\label{utility_gain_mlisa_and_rational}
\end{figure}

\begin{figure}%[!t]
\centering
\includegraphics[width=3.5in]{figures/utility_ratio.eps}
\caption{Ratio of Utility Gain DLISA and Rational}
\label{utility_gain_mlisa_and_rational_ratio}
\end{figure}

@@

\begin{table}[ht]
\caption{Number of communities that misses the optimal decision, out of 1,000 communities} % title of Table
\centering % used for centering table
\begin{tabular}{|c|c|} % centered columns (4 columns)
\hline %inserts double horizontal lines
 Method&Miss \\ [0.5ex] % inserts table
%heading
\hline % inserts single horizontal line
 DLISA r=0.05& 375 \\ % inserting body of the table
 DLISA r=0.07& 137 \\
 DLISA r=0.10& 6 \\
 DLISA r=0.20& 6 \\
Rational Method& 717 \\
Greedy Method& 828 \\ [1ex] % [1ex] adds vertical space
\hline %inserts single line
\end{tabular}
\label{fail_rate} % is used to refer this table in the text
\end{table}

In order to evaluate the performance of the mechanism, we used \emph{Receiver Operating Characteristic (ROC) curve}, which is a graphical plot illustrating the true negative rate against the false positive rate at various threshold settings in classifier systems. In order to classify our communities' selection strategies correctly, for each community, we evaluated the training process by replacing the community in the set with the closest one, from which it gets the strategy profile. If the actions are the same and the same utility levels are gained, we classify the decision as correct. Otherwise, it is classified as a wrong decision. \emph{AUC}, the area under the \emph{ROC curve}, is equal to the probability that a classifier will rank a randomly chosen positive instance higher than a randomly chosen negative one, and the higher number reflects better performance from the better solution.  Figure \ref{roc5} illustrates the \emph{ROC curve} evaluation of the DLISA decision making mechanism. We compare our method with two other methods. The \emph{rational} method is based on the assumption that communities, as rational agents, join a community that increases their utility. The \emph{greedy} method only looks up the available list of communities and simply joins the community that maximizes its utility without considering any long-term strategy or  other communities' acceptance scenarios. Figure \ref{roc5} compares the results for all methods. The two other methods have very high failure rates compared to our method. Table \ref{fail_rate} illustrates the number of communities that failed to find the optimal collaboration group. The results support the need for a long-term training model in a successful decision making process.

@@

All the proposed frameworks share a common aspect, which is providing the solution based on assumption of having complete information of all services and performing evaluations based on a large number of input each time they want to adopt a strategic decision making process. 
So basically These solutions generally suffer from high complexity, which makes decision making impossible in an on-demand fashion, or they simplify important aspects to make it practical in the real world, thereby hurting the decision making performance. We address this issue by introducing DLISA a framework that operates based on a trained model that regulates web service agents' decision making process in terms of cooperating with one another. After being trained, web services get to compute expectations as utilities they would gain while cooperating with communities of different characteristics. Therefore web services and communities can make prudent decisions when inviting a web service to join or accepting a join inquiry initiated from a web service. In general, DLISA equips web services with efficient methods for foreseeing how their choices will impact their long-term and short-term goals; therefore, opting for best decision available.

>>>>

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
%\title{A Distributed Mechanism for Intelligent \\ Web Service Community Formation}
\title{DDM: Distributed Decision Making Model for Dynamic Formation of Web services Communities}
%
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%
%
%\IEEEcompsocitemizethanks is a special \thanks that produces the bulleted
% lists the Computer Society journals use for "first footnote" author
% affiliations. Use \IEEEcompsocthanksitem which works much like \item
% for each affiliation group. When not in compsoc mode,
% \IEEEcompsocitemizethanks becomes like \thanks and
% \IEEEcompsocthanksitem becomes a line break with idention. This
% facilitates dual compilation, although admittedly the differences in the
% desired content of \author between the different types of papers makes a
% one-size-fits-all approach a daunting prospect. For instance, compsoc
% journal papers have the author affiliations above the "Manuscript
% received ..."  text while in non-compsoc journals this is reversed. Sigh.

@@

Web services are loosely-coupled business applications willing to cooperate in distributed settings within different groups called communities. Communities aim to provide web services with better visibility, efficiency, market share and total payoff. A number of mechanisms and models have been recently proposed to aggregate web
services and make them cooperate within their communities. However, the solutions mostly focus on short term goals. Moreover, these solutions generally suffer from high computational complexity, which makes decision making impossible in an on-demand fashion. In this paper, we propose a strategic decision making mechanism that regulates web service agents' decision making process in terms of cooperating with one another. This model first generates a trained set of data based on information obtained from large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc. Utilizing the training model, the decision making mechanism implements a decision tree of possible viable strategies and their long-term expected utility gain.
%Utilizing the training model, the decision making mechanism implements a decision tree with an estimation of long-term utility gain for the web services. Communities can used the trained model and instantly choose best-response strategies considering their long-term gain. 
Our findings show that using this data, communities of web services can efficiently find the appropriate web service to invite cooperating with them as well as a single web service can find best communities to target joining them. In further details, after being trained, web services get to compute expectations as utilities they would gain while cooperating with communities of different characteristics. In contrast, communities can consider the training into account and analyze the characteristics of different individual web services and make prudent decisions while inviting a web service to join or accepting a join inquiry initiated from a web service. In general, DDM equips web services with efficient methods of foreseeing how their choices of actions would impact their long-term and short-term goals, therefore opting for best decision available. The experimental results show that our algorithms provide web services and community owners, in real-world-like environments, with applicable and near-perfect decision making mechanisms.

%In the last few years, communities of services have been studied in a certain numbers of proposals as virtual pockets of similar expertise. The motivation is to provide these services with high chance of discovery through better visibility, and to enhance their capabilities when it comes to provide requested functionalities. We introduce DDM (Machine Learning-based Intelligent Service Agents) community framework that operates based on a trained model that regulates web service agents' decision making process in terms of cooperating with one another. This model uses the trained data in the form of information obtained from large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc. The training model deploys logistic regression algorithm to build hypothesis function that can thoroughly address the aforementioned research problems. Our findings show that communities of web services can efficiently find the appropriate web service to invite cooperating with them as well as a single web service can find best communities to target joining them. In further details, after being trained, web services get to compute expectations as utilities they would gain while cooperating with communities of different characteristics. In contrast, communities can consider the training into account and analyze the characteristics of different individual web services and make prudent decisions while inviting a web service to join or accepting a join inquiry initiated from a web service. In general, DDM equips web services with efficient methods of foreseeing how their choices of actions would impact their long-term and short-term goals, therefore opting for best decision available.

@@

% Note that keywords are not normally used for peer review papers.
\begin{keywords}
Web services; Community of services; Distributed Decision Making;
\end{keywords}}

@@

In this paper, we introduce DDM (Distributed Learning-based Intelligent Service Agents) community framework that operates based on a decision model that regulates web service agents' decision making process in terms of cooperating with one another. The decision model in extracted from a data model in the form of information obtained from a large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc. 
%The training model deploys a logistic regression algorithm to build a hypothesis function that can thoroughly address the aforementioned research problems. 
The decision model utilizes web services with enough information to efficiently decide and predict the outcome of their moves amongst the available services accessible to them. This model works in distributed manner in which our services are self-sufficient in decision making process and do not rely on a centralized decision maker process. Our findings show that communities of web services can efficiently find the appropriate web service to invite cooperating with them as well as allowing a single web service to find the best communities to join them. Furthermore, the decision model provides web services with expectations of utilities they would gain while cooperating with communities of different characteristics. In contrast, communities can consider the decision model and analyze the characteristics of different individual web services and make prudent decisions when inviting a web service to join or accepting a join inquiry initiated from a web service. In general, DDM equips web services with efficient methods for foreseeing how their choices will impact their long-term and short-term goals; therefore, opting for best decision available.

In further detail, DDM is applicable for any sort of intelligent agent-based model. To effectively train web services, we used real data sets to extract web services' individual characteristics and used them to measure outcomes when they cooperate with one another. The data set has been extracted by real-world QoS evaluation results from 142 users on 4,532 Web services on 64 different time slots. Combining these data based on each web service point of view on different time slots, we acquired 5 different unique features for 4,532 web services. Engineering and extracting these features, we gathered functional and cooperative features for both individual web services and communities in different time slots. We were able to investigate the path a web service might take to achieve the best utility out of effective interaction with others. All paths and the outcomes are labeled to be utilized in the training model. Using cross validation sets, web services are able to compute the optimal hypothesis function (using logistic regression) that can be used to predict outcomes of cooperative work with other individual web services or communities. Our findings show that web services equipped with DDM have by far better outcomes in the form of cooperative service providers than the ones that either do not cooperate or randomly find communities to join.

@@

\section{Preliminaries and Problem Statement}\label{s:preliminaries}
In this section, we first present the architecture of DDM. We explore the characteristics of intelligent service agents and the features we extract for training. To do this, we first discuss some preliminaries.

@@

\subsubsection{Feature Normalization}\label{sss:fn}

	We normalize the range of these features so that each feature contributes approximately proportionately to the final utility outcome value. We adopt the \emph{standardization} method. We subtract the \emph{mean} from each feature then we divide the values of each feature by its \emph{standard deviation}.

%$HI = \overline{HI}$

@@

\begin{algorithm}
\DontPrintSemicolon
\KwIn{$\langle r, gain^t_{n,n}, CFVS \rangle$ learning rate $r$, $|N \times N \times T|$ gain matrix, community feature vector}
\KwOut{A set of \emph{root} nodes of the decision trees}
$k \gets 1$\;
$nodes[N] \gets$ initialize $N$ tree nodes representing each community in CFVS\;
\For{$t \gets 1$ \textbf{to} $T$} {
	$k \gets 1 + round (r \times t)$\;
  \For{all $C_i \in CFVS$} {
	  \For{all $C_j \in L^t(C_i, k)$} {
      % The "l" before the If makes it so it does not expand to a second line
      \If{$C_i \in L^t(C_j, k)$}{
        $C_k \gets C_i \cup C_j$\;
				add $C_k$ to $CFVS$ set\;
				initiate $node_k$, representing $C_k$\;
				$nodes_i.addChild (node_k)$\;
				$nodes_j.addChild (node_k)$\;
      }
%      \Else{
%        $j \gets j + 1$\;
%      }			
		}
  }
%  $i \gets i + 1$\;
}
\Return{nodes}\;
\caption{{\sc DDM Decision Tree Algorithm}}
\label{algo:dectree}
\end{algorithm}

\subsection{Decision Tree Creation Complexity}\label{ss:complexity}
Here we analyze the computational complexity of the DDM decision tree creation algorithm on each time iteration $t$. Computing top $k$ preferred communities for $C_i$ in $L^t(C_i, k)$ requires an $O(n.log(n))$ sort time. $C_i$ has a result set of size $|k|$, and for each of those $k$ communities we need to check against their $k$ top preferred communities. Considering we already have the list sorted, line 6 in algorithm runs $O(k \times n.log(n))$ times. Doing this search for all communities in $|CFVS|$ set $n$ times (line 5), the overall order of complexity of the algorithm in regards with $n$ and $k$ is: $O(k^2 \times n^2.log(n))$.

\section{Experiments}\label{s:experiments}
We implemented DDM in Java\footnote{Source code of implementation and data is available at: \emph{https://github.com/Marooned202/DDM}}. We have extracted the set of features for 4532 web services in 64 different time slots through a data set provided by \cite{10.1109/ISSRE.2011.17}. By choosing 86 web services out of these sets and choosing a subset of all possible combinations of sizes 2, 3, and 4 of these 86 web services, we have chosen 10,000 communities and evaluated the feature vectors and utilities they can have in 64 different time slots. This provides us with the initial training feature set of size $|CFVS| = 10,000$ communities. Based on Equation \ref{u_c_load} the utility of these communities are estimated, and the gain matrix $|10000 \times~ 10000|$ of all possible ways of merging these 10,000 communities, is generated\footnote {The template vector and gain matrix generated are available at \emph{https://github.com/Marooned202/DDM/tree/master/wsds/data/run}}, and each community has the ordered preference among other communities known in the set.

We let communities and web services adopt their strategies based on our $DDM$ decision making mechanism. Based on the decisions adopted, each community will generate a decision tree profile. We let DDM run four times with different $r$ rates of 0.05, 0.07, 0.10 and 0.20. With the slow rate of $r = 0.05$, we increase $k$ in Equation \ref{u_c_normal} for every 20 time frames, which will happen only three times in our 64-step experiment. In the case of $r = 0.20$, k increases much faster, at a rate of once every 5 time frames, which increases the complexity of the $L^t(C_i,k)$ search for each community in the $CFVS$ set.

@@

\begin{figure}%[!t]
\centering
\includegraphics[width=3.5in]{figures/utility_gain_r.eps}
\caption{DDM Utility Gain Value}
\label{utility_gain_value}
\end{figure}

\begin{figure}%[!t]
\centering
\includegraphics[width=3.5in]{figures/utility_ratio_r.eps}
\caption{DDM Utility Gain Ratio}
\label{utility_gain_ratio}
\end{figure}

@@

\begin{figure}%[!t]
\centering
\includegraphics[width=3.5in]{figures/utility_gain.eps}
\caption{Utility Gain DDM and Rational}
\label{utility_gain_mlisa_and_rational}
\end{figure}

\begin{figure}%[!t]
\centering
\includegraphics[width=3.5in]{figures/utility_ratio.eps}
\caption{Ratio of Utility Gain DDM and Rational}
\label{utility_gain_mlisa_and_rational_ratio}
\end{figure}

@@

\begin{table}[ht]
\caption{Number of communities that misses the optimal decision, out of 1,000 communities} % title of Table
\centering % used for centering table
\begin{tabular}{|c|c|} % centered columns (4 columns)
\hline %inserts double horizontal lines
 Method&Miss \\ [0.5ex] % inserts table
%heading
\hline % inserts single horizontal line
 DDM r=0.05& 375 \\ % inserting body of the table
 DDM r=0.07& 137 \\
 DDM r=0.10& 6 \\
 DDM r=0.20& 6 \\
Rational Method& 717 \\
Greedy Method& 828 \\ [1ex] % [1ex] adds vertical space
\hline %inserts single line
\end{tabular}
\label{fail_rate} % is used to refer this table in the text
\end{table}

In order to evaluate the performance of the mechanism, we used \emph{Receiver Operating Characteristic (ROC) curve}, which is a graphical plot illustrating the true negative rate against the false positive rate at various threshold settings in classifier systems. In order to classify our communities' selection strategies correctly, for each community, we evaluated the training process by replacing the community in the set with the closest one, from which it gets the strategy profile. If the actions are the same and the same utility levels are gained, we classify the decision as correct. Otherwise, it is classified as a wrong decision. \emph{AUC}, the area under the \emph{ROC curve}, is equal to the probability that a classifier will rank a randomly chosen positive instance higher than a randomly chosen negative one, and the higher number reflects better performance from the better solution.  Figure \ref{roc5} illustrates the \emph{ROC curve} evaluation of the DDM decision making mechanism. We compare our method with two other methods. The \emph{rational} method is based on the assumption that communities, as rational agents, join a community that increases their utility. The \emph{greedy} method only looks up the available list of communities and simply joins the community that maximizes its utility without considering any long-term strategy or  other communities' acceptance scenarios. Figure \ref{roc5} compares the results for all methods. The two other methods have very high failure rates compared to our method. Table \ref{fail_rate} illustrates the number of communities that failed to find the optimal collaboration group. The results support the need for a long-term training model in a successful decision making process.

@@

All the proposed frameworks share a common aspect, which is providing the solution based on assumption of having complete information of all services and performing evaluations based on a large number of input each time they want to adopt a strategic decision making process. 
So basically These solutions generally suffer from high complexity, which makes decision making impossible in an on-demand fashion, or they simplify important aspects to make it practical in the real world, thereby hurting the decision making performance. We address this issue by introducing DDM a framework that operates based on a trained model that regulates web service agents' decision making process in terms of cooperating with one another. After being trained, web services get to compute expectations as utilities they would gain while cooperating with communities of different characteristics. Therefore web services and communities can make prudent decisions when inviting a web service to join or accepting a join inquiry initiated from a web service. In general, DDM equips web services with efficient methods for foreseeing how their choices will impact their long-term and short-term goals; therefore, opting for best decision available.
